---
title: "Data605Week11"
author: "Huang, Angus"
date: "November 11, 2017"
output: html_document
---

Check the first 6 rows of the cars dataset. 

```{r}
head(cars)
#summary(cars$dist)
```

Summary of linear regression model. The y-intercept is -17.579 and the slope is 3.932.
"The residuals are the differences between the actual measured values and the corresponding values on the fitted regression line. A good model's residual should be roughly balanced around from the mean of zero."

The standard error should also be five to ten times smaller thand the corresponding coefficient for a good model.
```{r}
lmcar <-lm(cars$dist ~ cars$speed)
lmcar
summary(lmcar)
```


```{r}
{plot(cars$speed,cars$dist,main = "1920 Cars speed and number of Feet Taken to Stop",
      col = 'navyblue', pch = 16, xlab = "Speed (mph)", ylab = "Stopping Distance (feet)")
abline(lmcar, col = "red")}
```

Plotting the residuals from above model to analyze 
```{r}
plot(fitted(lmcar),resid(lmcar),col = 'navyblue', pch = 16, main = "The residual values vs. input values: \n well fitted model will have uniformly distribution around zero")
```
Plotting Q-Q plot: quantile-versus-quantile.
Q-Q plot is used for visually examining whether the residuals are normally distributed.
Notes: points forming along the qqline indicates normally distributed residuals. 

```{r}
qqnorm(resid(lmcar))
qqline(resid(lmcar), col = "red")
```